\plaintitle

### 2025-05-21 docs/style/article-body.tex
table position fix

\begin{figure*}[ht] \centering
\includegraphics[width=\textwidth]{img/testscript.png} \caption{A brief overview
of the testscript architecture.} \label{fig:testscript-architecture}
\end{figure*}

@@

\textbf{Iteration 1 - Data Structures:}

\begin{table}[ht] \centering \begin{tabular}{|c|c|c|} \hline \textbf{Bit size} &
\textbf{Teensy ($\mu$s)} & \textbf{Pico ($\mu$s)} \\ \hline 64 & 13.1564 &
106.3914 \\ 512 & 788.3139 & 5302.4979 \\ 1024 & 3124.0580 & 21111.2163 \\
\hline \end{tabular} \caption{Execution times for different bit sizes on Teensy
and Pico} \label{tab:iter1} \end{table}

Table \ref{tab:iter1} presents the average execution time of iteration 1 on both Teensy 4.1 and Raspberry Pico Pi 2 across thre input sizes. The Teensy consistently outperforms the Pico, with the gap widening as the bit size increases.

\textbf{Iteration 2 - Bitshifting:}

\begin{table}[ht]\begin{tabular}{|c|c|} \hline \textbf{Bit size} &
\multicolumn{1}{c|}{\textbf{Avg ($\mu s$)}} \\ \hline 64 & 16.4689 \\ 512 &
1006.6255 \\ 1024 & 3996.5972 \\ \hline \end{tabular}
\label{tab:iter2}\end{table}

@@

Additionally, the isolated effect of applying a single bitmask operation \texttt{\&\ 1} was evaluated. This resulted in a slight reduction in average execution time, from \texttt{13.1564\ µs} to \texttt{13.1000\ µs}, although this specific result is not included in the tables above.

\textbf{Iteration 3 - Batching and Hardware optimization:}

\begin{table}[ht]\begin{tabular}{|c|c|} \hline \textbf{Bit size} &
\multicolumn{1}{c|}{\textbf{Avg ($\mu s$)}} \\ \hline 64/64 & 43.0760 \\ 512/512
& 2663.8194 \\ 1024/1024 & 10513.1767 \\ \hline \end{tabular}
\label{tab:iter3}\end{table}

Table \ref{tab:iter3} presents the average execution time of iteration 3 on the Teensy 4.1 for varying batching and bit sizes. Additionally, when performing the same 1024/1024-bit operation, the Raspberry Pi Pico 2 showed average execution time of \texttt{80806.006\ µs} indicating a substantially lower throughput compared to the Teensy.

@@

\textbf{Iteration 4 - Loop unrolling:}

\begin{table}[ht]\begin{tabular}{|c|c|c|} \hline \textbf{Bit size} &
\multicolumn{1}{c|}{\textbf{Teensy ($\mu s$)}} &
\multicolumn{1}{c|}{\textbf{Pico ($\mu s$)}} \\ \hline 64 & 9.7017 & 70.7402 \\
512 & 551.6358 & 3978.1928 \\ 1024 & 2195.1979 & 15830.8784 \\ \hline
\end{tabular} \label{tab:iter4}\end{table}

@@

In addition to the results presented in Table \ref{tab:iter4}, a further tests was conducted on the Teensy using a single-loop unrolled implementation for the 64-bit size, resulting in an average execution time of \texttt{6.6626\ µs}. An additional fully unrolled variant, where loops were entirely eliminated, produced a measured execution time of \texttt{0.0491\ µs}. However, this measurement was later determined to be invalid due to packaging error.

\textbf{Iteration 5 - Removal of vector usage:}

\begin{table}[ht]\begin{tabular}{|c|c|c|} \hline \textbf{Bit size} &
\multicolumn{1}{c|}{\textbf{Teensy ($\mu s$)}} &
\multicolumn{1}{c|}{\textbf{Pico ($\mu s$)}} \\ \hline 64 & 0.0501 & 0.2175 \\
\hline \end{tabular} \label{tab:iter5}\end{table}

@@

\textbf{Iteration 6 - Data type exploration:}

\begin{table}[ht]\begin{tabular}{|c|c|} \hline \textbf{Data structure} &
\multicolumn{1}{c|}{\textbf{Avg ($\mu s$)}} \\ \hline array & 0.4284 \\
unordered_map & 31.5090 \\ bitset & 0.0474 \\ \hline \end{tabular}
\label{tab:iter6}\end{table}

Table \ref{tab:iter6} presents the results of iteration 6, which was introduced to address the structural limitations encountered in iteration 5. Specifically, the fixed-width output constrains imposed by the removal of vector. In this iteration, alternative data structures were evaluated. Vector-based approach from iteration 1 serving as a baseline for comparison.

>>>>

\begin{figure*}[!t] \centering
\includegraphics[width=\textwidth]{img/testscript.png} \caption{A brief overview
of the testscript architecture.} \label{fig:testscript-architecture}
\end{figure*}

@@

\vspace{1em}

\begin{table}[ht] \centering \caption{Iteration 1 - Data Structures}
\label{tab:iter1}
\begin{tabularx}{\columnwidth}{|>{\centering\arraybackslash}X|>{\centering\arraybackslash}X|>{\centering\arraybackslash}X|}
\hline \textbf{Bit size} & \textbf{Teensy ($\mu$s)} & \textbf{Pico ($\mu$s)} \\
\hline 64 & 13.1564 & 106.3914 \\ 512 & 788.3139 & 5302.4979 \\ 1024 & 3124.0580
& 21111.2163 \\ \hline \end{tabularx} \end{table}

Table \ref{tab:iter1} presents the average execution time of iteration 1 on both Teensy 4.1 and Raspberry Pico Pi 2 across the input sizes. The Teensy consistently outperforms the Pico, with the gap widening as the bit size increases.

\begin{table}[ht] \centring \caption{Iteration 2 - Bitshifting}
\label{tab:iter2}
\begin{tabularx}{\columnwidth}{|>{\centering\arraybackslash}X|>{\centering\arraybackslash}X|}
\hline \textbf{Bit size} & \multicolumn{1}{c|}{\textbf{Avg ($\mu s$)}} \\ \hline
64 & 16.4689 \\ 512 & 1006.6255 \\ 1024 & 3996.5972 \\ \hline \end{tabularx}
\end{table}

@@

Additionally, the isolated effect of applying a single bitmask operation \texttt{\&\ 1} was evaluated. This resulted in a slight reduction in average execution time, from \texttt{13.1564} \(\mu s\) to \texttt{13.1000} \(\mu s\), although this specific result is not included in the tables above.

\begin{table}[H] \centring \caption{Iteration 3 - Batching and Hardware
optimization} \label{tab:iter3}
\begin{tabularx}{\columnwidth}{|>{\centering\arraybackslash}X|>{\centering\arraybackslash}X|}
\hline \textbf{Bit size} & \multicolumn{1}{c|}{\textbf{Avg ($\mu s$)}} \\ \hline
64/64 & 43.0760 \\ 512/512 & 2663.8194 \\ 1024/1024 & 10513.1767 \\ \hline
\end{tabularx} \end{table}

Table \ref{tab:iter3} presents the average execution time of iteration 3 on the Teensy 4.1 for varying batching and bit sizes. Additionally, when performing the same 1024/1024-bit operation, the Raspberry Pi Pico 2 showed average execution time of \texttt{80806.006} \(\mu s\) indicating a substantially lower throughput compared to the Teensy.

@@

\vspace{1em}

\begin{table}[ht] \centring \caption{Iteration 4 - Loop unrolling}
\label{tab:iter4}
\begin{tabularx}{\columnwidth}{|>{\centering\arraybackslash}X|>{\centering\arraybackslash}X|>{\centering\arraybackslash}X|}
\hline \textbf{Bit size} & \multicolumn{1}{c|}{\textbf{Teensy ($\mu s$)}} &
\multicolumn{1}{c|}{\textbf{Pico ($\mu s$)}} \\ \hline 64 & 9.7017 & 70.7402 \\
512 & 551.6358 & 3978.1928 \\ 1024 & 2195.1979 & 15830.8784 \\ \hline
\end{tabularx} \end{table}

@@

In addition to the results presented in Table \ref{tab:iter4}, a further tests was conducted on the Teensy using a single-loop unrolled implementation for the 64-bit size, resulting in an average execution time of \texttt{6.6626} \(\mu s\). An additional fully unrolled variant, where loops were entirely eliminated, produced a measured execution time of \texttt{0.0491} \(\mu s\). However, this measurement was later determined to be invalid due to packaging error.

\vspace{1em}

\begin{table}[ht] \centring \caption{Iteration 5 - Removal of vector usage}
\label{tab:iter5}
\begin{tabularx}{\columnwidth}{|>{\centering\arraybackslash}X|>{\centering\arraybackslash}X|>{\centering\arraybackslash}X|}
\hline \textbf{Bit size} & \multicolumn{1}{c|}{\textbf{Teensy ($\mu s$)}} &
\multicolumn{1}{c|}{\textbf{Pico ($\mu s$)}} \\ \hline 64 & 0.0501 & 0.2175 \\
\hline \end{tabularx} \end{table}

@@

\vspace{1em}

\begin{table}[H] \centring \caption{Iteration 6 - Data type exloration}
\label{tab:iter6}
\begin{tabularx}{\columnwidth}{|>{\centering\arraybackslash}X|>{\centering\arraybackslash}X|}
\hline \textbf{Data structure} & \multicolumn{1}{c|}{\textbf{Avg ($\mu s$)}} \\
\hline array & 0.4284 \\ unordered_map & 31.5090 \\ bitset & 0.0474 \\ \hline
\end{tabularx} \end{table}

Table \ref{tab:iter6} presents the results of iteration 6 using 64 bit size, which was introduced to address the structural limitations encountered in iteration 5. Specifically, the fixed-width output constrains imposed by the removal of vector. In this iteration, alternative data structures were evaluated. Vector-based approach from iteration 1 serving as a baseline for comparison.

Additionally, 128 bit size were tested resulting in \texttt{179.8712} \(\mu s\).

### 2025-05-21 docs/style/article-final.tex
table position fix

% Load basic packages
\usepackage{balance}       % to better equalize the last page
\usepackage{graphics}      % for EPS, load graphicx instead 
\usepackage[T1]{fontenc}   % for umlauts and other diaeresis
\usepackage{txfonts}
\usepackage{mathptmx}
\usepackage[pdflang={en-US},pdftex]{hyperref}
\usepackage{color}
\usepackage{booktabs}
\usepackage{textcomp}
\usepackage{tikz}
\usetikzlibrary{positioning}
\usepackage{algorithm}
\usepackage{algorithmic}

% Some optional stuff you might like/need.
\usepackage{microtype}        % Improved Tracking and Kerning
% \usepackage[all]{hypcap}    % Fixes bug in hyperref caption linking
\usepackage{ccicons}          % Cite your images correctly!
% \usepackage[utf8]{inputenc} % for a UTF8 editor only

@@

\begin{figure*}[ht] \centering
\includegraphics[width=\textwidth]{img/testscript.png} \caption{A brief overview
of the testscript architecture.} \label{fig:testscript-architecture}
\end{figure*}

\subsubsection{6.1 Phase one}\label{phase-one-1}

\textbf{Iteration 1 - Data Structures:}

\begin{tabular}{|c|c|c|} \hline \textbf{Bit size} &
\multicolumn{1}{c|}{\textbf{Teensy ($\mu s$)}} &
\multicolumn{1}{c|}{\textbf{Pico ($\mu s$)}} \\ \hline 64 & 13.1564 & 106.3914
\\ 512 & 788.3139 & 5302.4979 \\ 1024 & 3124.0580 & 21111.2163 \\ \hline
\caption{A brief overview of the testscript architecture.} \label{tab:iter1}

\end{tabular}

Table \ref{tab:iter1} presents the average execution time of iteration 1 on both Teensy 4.1 and Raspberry Pico Pi 2 across thre input sizes. The Teensy consistently outperforms the Pico, with the gap widening as the bit size increases.

\textbf{Iteration 2 - Bitshifting:}

\begin{tabular}{|c|c|} \hline \textbf{Bit size} &
\multicolumn{1}{c|}{\textbf{Avg ($\mu s$)}} \\ \hline 64 & 16.4689 \\ 512 &
1006.6255 \\ 1024 & 3996.5972 \\ \hline \end{tabular}

\label{tab:iter2}

@@

Additionally, the isolated effect of applying a single bitmask operation \texttt{\&\ 1} was evaluated. This resulted in a slight reduction in average execution time, from \texttt{13.1564\ µs} to \texttt{13.1000\ µs}, although this specific result is not included in the tables above.

\textbf{Iteration 3 - Batching and Hardware optimization:}

\begin{tabular}{|c|c|} \hline \textbf{Bit size} &
\multicolumn{1}{c|}{\textbf{Avg ($\mu s$)}} \\ \hline 64/64 & 43.0760 \\ 512/512
& 2663.8194 \\ 1024/1024 & 10513.1767 \\ \hline \end{tabular}

\label{tab:iter3}

Table \ref{tab:iter3} presents the average execution time of iteration 3 on the Teensy 4.1 for varying batching and bit sizes. Additionally, when performing the same 1024/1024-bit operation, the Raspberry Pi Pico 2 showed average execution time of \texttt{80806.006\ µs} indicating a substantially lower throughput compared to the Teensy.

\subsubsection{6.2 Phase two}\label{phase-two-1}

\textbf{Iteration 4 - Loop unrolling:}

\begin{tabular}{|c|c|c|} \hline \textbf{Bit size} &
\multicolumn{1}{c|}{\textbf{Teensy ($\mu s$)}} &
\multicolumn{1}{c|}{\textbf{Pico ($\mu s$)}} \\ \hline 64 & 9.7017 & 70.7402 \\
512 & 551.6358 & 3978.1928 \\ 1024 & 2195.1979 & 15830.8784 \\ \hline
\end{tabular}

\label{tab:iter4}

@@

In addition to the results presented in Table \ref{tab:iter4}, a further tests was conducted on the Teensy using a single-loop unrolled implementation for the 64-bit size, resulting in an average execution time of \texttt{6.6626\ µs}. An additional fully unrolled variant, where loops were entirely eliminated, produced a measured execution time of \texttt{0.0491\ µs}. However, this measurement was later determined to be invalid due to packaging error.

\textbf{Iteration 5 - Removal of vector usage:}

\begin{tabular}{|c|c|c|} \hline \textbf{Bit size} &
\multicolumn{1}{c|}{\textbf{Teensy ($\mu s$)}} &
\multicolumn{1}{c|}{\textbf{Pico ($\mu s$)}} \\ \hline 64 & 0.0501 & 0.2175 \\
\hline \end{tabular}

\label{tab:iter5}

@@

\textbf{Iteration 6 - Data type exploration:}

\begin{tabular}{|c|c|} \hline \textbf{Data structure} &
\multicolumn{1}{c|}{\textbf{Avg ($\mu s$)}} \\ \hline array & 0.4284 \\
unordered_map & 31.5090 \\ bitset & 0.0474 \\ \hline \end{tabular}

\label{tab:iter6}

Table \ref{tab:iter6} presents the results of iteration 6, which was introduced to address the structural limitations encountered in iteration 5. Specifically, the fixed-width output constrains imposed by the removal of vector. In this iteration, alternative data structures were evaluated. Vector-based approach from iteration 1 serving as a baseline for comparison.

\subsection{7 CONCLUSION}\label{conclusion}

\subsection{CHANGELOG}\label{changelog}

>>>>

% Load basic packages
\usepackage{balance}       % to better equalize the last page
\usepackage{graphics}      % for EPS, load graphicx instead 
\usepackage[T1]{fontenc}   % for umlauts and other diaeresis
\usepackage{txfonts}
\usepackage{mathptmx}
\usepackage[pdflang={en-US},pdftex]{hyperref}
\usepackage{color}
\usepackage{booktabs}
\usepackage{textcomp}
\usepackage{tikz}
\usetikzlibrary{positioning}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{caption}
\usepackage{tabularx}
\usepackage{array}
\usepackage{float}
% Some optional stuff you might like/need.
\usepackage{microtype}        % Improved Tracking and Kerning
% \usepackage[all]{hypcap}    % Fixes bug in hyperref caption linking
\usepackage{ccicons}          % Cite your images correctly!
% \usepackage[utf8]{inputenc} % for a UTF8 editor only

@@

\begin{figure*}[!t] \centering
\includegraphics[width=\textwidth]{img/testscript.png} \caption{A brief overview
of the testscript architecture.} \label{fig:testscript-architecture}
\end{figure*}

\hypertarget{phase-one-1}{%
\subsubsection{6.1 Phase one}\label{phase-one-1}}

\vspace{1em}

\begin{table}[ht] \centering \caption{Iteration 1 - Data Structures}
\label{tab:iter1}
\begin{tabularx}{\columnwidth}{|>{\centering\arraybackslash}X|>{\centering\arraybackslash}X|>{\centering\arraybackslash}X|}
\hline \textbf{Bit size} & \textbf{Teensy ($\mu$s)} & \textbf{Pico ($\mu$s)} \\
\hline 64 & 13.1564 & 106.3914 \\ 512 & 788.3139 & 5302.4979 \\ 1024 & 3124.0580
& 21111.2163 \\ \hline \end{tabularx} \end{table}

Table \ref{tab:iter1} presents the average execution time of iteration 1 on both Teensy 4.1 and Raspberry Pico Pi 2 across the input sizes. The Teensy consistently outperforms the Pico, with the gap widening as the bit size increases.

\begin{table}[ht] \centring \caption{Iteration 2 - Bitshifting}
\label{tab:iter2}
\begin{tabularx}{\columnwidth}{|>{\centering\arraybackslash}X|>{\centering\arraybackslash}X|}
\hline \textbf{Bit size} & \multicolumn{1}{c|}{\textbf{Avg ($\mu s$)}} \\ \hline
64 & 16.4689 \\ 512 & 1006.6255 \\ 1024 & 3996.5972 \\ \hline \end{tabularx}
\end{table}

@@

Additionally, the isolated effect of applying a single bitmask operation \texttt{\&\ 1} was evaluated. This resulted in a slight reduction in average execution time, from \texttt{13.1564} \(\mu s\) to \texttt{13.1000} \(\mu s\), although this specific result is not included in the tables above.

\begin{table}[H] \centring \caption{Iteration 3 - Batching and Hardware
optimization} \label{tab:iter3}
\begin{tabularx}{\columnwidth}{|>{\centering\arraybackslash}X|>{\centering\arraybackslash}X|}
\hline \textbf{Bit size} & \multicolumn{1}{c|}{\textbf{Avg ($\mu s$)}} \\ \hline
64/64 & 43.0760 \\ 512/512 & 2663.8194 \\ 1024/1024 & 10513.1767 \\ \hline
\end{tabularx} \end{table}

Table \ref{tab:iter3} presents the average execution time of iteration 3 on the Teensy 4.1 for varying batching and bit sizes. Additionally, when performing the same 1024/1024-bit operation, the Raspberry Pi Pico 2 showed average execution time of \texttt{80806.006} \(\mu s\) indicating a substantially lower throughput compared to the Teensy.

\hypertarget{phase-two-1}{%
\subsubsection{6.2 Phase two}\label{phase-two-1}}

\vspace{1em}

\begin{table}[ht] \centring \caption{Iteration 4 - Loop unrolling}
\label{tab:iter4}
\begin{tabularx}{\columnwidth}{|>{\centering\arraybackslash}X|>{\centering\arraybackslash}X|>{\centering\arraybackslash}X|}
\hline \textbf{Bit size} & \multicolumn{1}{c|}{\textbf{Teensy ($\mu s$)}} &
\multicolumn{1}{c|}{\textbf{Pico ($\mu s$)}} \\ \hline 64 & 9.7017 & 70.7402 \\
512 & 551.6358 & 3978.1928 \\ 1024 & 2195.1979 & 15830.8784 \\ \hline
\end{tabularx} \end{table}

@@

In addition to the results presented in Table \ref{tab:iter4}, a further tests was conducted on the Teensy using a single-loop unrolled implementation for the 64-bit size, resulting in an average execution time of \texttt{6.6626} \(\mu s\). An additional fully unrolled variant, where loops were entirely eliminated, produced a measured execution time of \texttt{0.0491} \(\mu s\). However, this measurement was later determined to be invalid due to packaging error.

\vspace{1em}

\begin{table}[ht] \centring \caption{Iteration 5 - Removal of vector usage}
\label{tab:iter5}
\begin{tabularx}{\columnwidth}{|>{\centering\arraybackslash}X|>{\centering\arraybackslash}X|>{\centering\arraybackslash}X|}
\hline \textbf{Bit size} & \multicolumn{1}{c|}{\textbf{Teensy ($\mu s$)}} &
\multicolumn{1}{c|}{\textbf{Pico ($\mu s$)}} \\ \hline 64 & 0.0501 & 0.2175 \\
\hline \end{tabularx} \end{table}

@@

\vspace{1em}

\begin{table}[H] \centring \caption{Iteration 6 - Data type exloration}
\label{tab:iter6}
\begin{tabularx}{\columnwidth}{|>{\centering\arraybackslash}X|>{\centering\arraybackslash}X|}
\hline \textbf{Data structure} & \multicolumn{1}{c|}{\textbf{Avg ($\mu s$)}} \\
\hline array & 0.4284 \\ unordered_map & 31.5090 \\ bitset & 0.0474 \\ \hline
\end{tabularx} \end{table}

Table \ref{tab:iter6} presents the results of iteration 6 using 64 bit size, which was introduced to address the structural limitations encountered in iteration 5. Specifically, the fixed-width output constrains imposed by the removal of vector. In this iteration, alternative data structures were evaluated. Vector-based approach from iteration 1 serving as a baseline for comparison.

Additionally, 128 bit size were tested resulting in \texttt{179.8712} \(\mu s\).

\hypertarget{conclusion}{%
\subsection{7 CONCLUSION}\label{conclusion}}

\hypertarget{changelog}{%
\subsection{CHANGELOG}\label{changelog}}
